---
title: "Data Analysis Report Study 1"
author: "Niklas Johannes"
date: "25/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      warning = FALSE,
                      cache = TRUE)
```

This file explains all data processing and analysis steps for Study 1 of [Project Title].
The RProject has a private library in order to make all steps computationally reproducible.
I use the `renv` package for this.
That means you will need to install the package and run the `renv::restore` command, see instructions [here](https://github.com/rstudio/renv).
```{r load_libraries}
# pacman makes it easier to load and install packages
if (!requireNamespace("pacman"))
  install.packages("pacman")

library(pacman)

# load packages
p_load(
  here,
  janitor,
  tidyverse
)

# set seed
set.seed(42)
```

```{r custom_functions}

```


# 1. Load data and wrangle data
First, we load the data.
For a codebook, see the [enter file name] file.
```{r load_data}
raw_data <- read_csv(
  here("data", "study1", "raw_data.csv")
  )
```

The variable names aren't in a nice format.
Notably, they all contain `_all_items_final` at the end and are in all upper case.
I will first remove the `_all_items_final` part from the variable names and then use the `janitor` package to get nicer variable names.
```{r clean_names}
# use a working file from now on
working_file <- raw_data

# remove variable name part
names(working_file) <-
  names(working_file) %>% 
  str_remove(., "_all_items_final")

# get variable names in snake case
working_file <- 
  clean_names(working_file)

# inspect data
glimpse(working_file)
```

Next, I add a food type category based on the subject number (`subjectnr` indicates the food ID):

* 1-80: vegan
* 81-160: vegetarian
* 161-240: meat-based
```{r add_food_type}
working_file <-
  working_file %>% 
  mutate(
    food_type = case_when(
      subjectnr %in% 1:80 ~ "vegan",
      subjectnr %in% 81:160 ~ "vegetarian",
      subjectnr %in% 161:240 ~ "meat_based"
    )
  ) %>% 
  rename( # give more sensible name for food ID
    "food_id" = "subjectnr"
  )
```

At this point, we also don't have the actual food names in the data set.
Although we don't necessarily need them in the analysis, I'll add them for completeness' sake.

The food label data set is in the long format, meaning I first need to get unique food names, then add them to working file.
```{r add_food_names}
# read the file with food names and features
food_labels <-
  read_csv(
    here("data", "study1", "food_labels.csv")
  )

# add food names to raw_data
working_file <-
  working_file %>% 
    add_column(
      food = unique(food_labels$food)
    ) %>% # reorder variable names
  select(food_id, food, everything())
```

Next, I create the total number of features produced per food item and the proportion of features for each item.
```{r total_features}
# add total features per item and remove ambigous and nonwords
working_file <-
  working_file %>%
  select(-ambiguous, -nonword) %>% 
  mutate(
    total = rowSums(select(., production:neg_coping))
  )

# add proportion of each feature in relation to total number of features
total_proportions <-
  working_file %>% 
  mutate_at(
    vars(production:neg_coping),
    list(~ . / total)
  )

# add an identifier of that variable name
names(total_proportions)[3:45] <-
  names(total_proportions %>% 
          select(production:neg_coping)) %>% 
  str_replace(., "$", "_proportion")

# add those proportion variables to working file
working_file <-
  left_join(
    working_file,
    total_proportions
  )
```

I repeat these two steps for the three main categories: consumption situations, non-consumption situations, and situation-independent situations.
```{r per_category_features}
# get total number of features per category
working_file <-
  working_file %>% 
    mutate(
      consumption_total = rowSums(select(., taste_flavor:neg_coping)),
      non_consumption_total = rowSums(select(., production:prep_stor, cult_embed)),
      situation_independent_total = rowSums(select(., ingred_cont:long_ter_neg, overall_pos_eval:linguistic))
    )

# now proportion of features in that category
category_proportions <-
  working_file %>% 
    mutate_at(
      vars(
        consumption_total,
        non_consumption_total,
        situation_independent_total
      ),
      list(~ . / total)
    ) %>% select(food_id, consumption_total:situation_independent_total)

# add an identifier for those variables
names(category_proportions)[2:4] <-
  names(category_proportions %>% 
  select(-food_id)) %>% 
  str_replace(., "total", "proportion")

# add those proportion variables to working file
working_file <-
  left_join(
    working_file,
    category_proportions,
    by = c("food_id")
  )
```

Last, I do the same for the different sub-categories of consumption situations: sensory & reward, immediate positive consequences, immediate negative consequences, and contextual features.
```{r per_sub_category_features}
# get total number of features per sub-category
working_file <-
  working_file %>% 
    mutate(
      sensory_total = rowSums(select(., taste_flavor:action)),
      positive_total = rowSums(select(.,
                                      pos_conform_goals,
                                      pos_social_goals,
                                      pos_bodily_conseq:pos_coping)),
      negative_total = rowSums(select(.,
                                neg_conform_goals,
                                neg_social_goals,
                                neg_bodily_conseq:neg_coping)),
      contextual_total = rowSums(select(., cont_bodily:cont_consumable))
    )

# now proportion of features in that category
sub_category_proportions <-
  working_file %>% 
    mutate_at(
      vars(sensory_total:contextual_total),
      list(~ . / total)
    ) %>% select(food_id, sensory_total:contextual_total)

# add an identifier for those variables
names(sub_category_proportions)[2:5] <-
  names(sub_category_proportions %>% 
  select(-food_id)) %>% 
  str_replace(., "total", "proportion")

# add those proportion variables to working file
working_file <-
  left_join(
    working_file,
    sub_category_proportions,
    by = c("food_id")
  )
```

Okay, now the file contains all information, but is not following tidy data conventions.
```{r tidy_data}
# first add an identifier to the feature count variables
names(working_file)[3:45] <-
  names(working_file %>% 
          select(production:neg_coping)) %>% 
  str_replace(., "$", "_count")

# then pivot to longer
working_file <-
  working_file %>% 
    pivot_longer(
      cols = c(production_count:neg_coping_count, production_proportion:neg_coping_proportion),
      names_to = c("feature", ".value"), # period to tell tidyr that that's where the value is
      names_sep = "_(?!.*_)", # looks for last underscore as the separator (which separates count and proportion)
      values_drop_na = TRUE
    ) %>% 
    select( #reorder variables
      food_id,
      food,
      food_type,
      feature:proportion,
      total,
      consumption_total:situation_independent_total,
      sensory_total:contextual_total,
      consumption_proportion:situation_independent_proportion,
      sensory_proportion:contextual_proportion
    ) %>% # assign proper variable types
    mutate_at(
      vars(contains("food"), feature),
      list(~ as.factor(.))
    )
```

# 2. Describe and visualize
Next, I visualize the different variables.
I'll start with the total number of features per foood.
Overall, it looks skewed with a long left tail, but without a really clear visual outlier.
```{r visualize_totals_per_food}
# number of features per food
ggplot(
  data = working_file,
  aes(
    x = reorder(food, count),
    y = count
  )
) +
  geom_bar(
    stat = "identity"
  )

# distribution of features per food
ggplot(data = working_file %>% group_by(food) %>% slice(1),
       aes(
         x = total
       )) + 
  geom_density(color = "darkgrey", 
               fill = "darkgrey")

# summary stats
working_file %>%
  pull(total) %>% 
  stat.desc()
```

Next, I'll do the same with the proportions proportions of consumption situtation features.
Looks pretty much like a binomial or beta distribution.
One food didn't have any of those features in its labels.
```{r visualize_consumption_features}
describe_visualize(
  working_file,
  consumption_proportion,
  FALSE,
  TRUE
)
```

Similar picture for non-consupmtion situations, but with more mass toward the middle, reflected in higher mean.
```{r visualize_non_consumption_features}
describe_visualize(
  working_file,
  non_consumption_proportion,
  FALSE,
  TRUE
)
```

Situation-independent features have a different distribution with a strong left skew.
```{r visualize_independent_features}
describe_visualize(
  working_file,
  situation_independent_proportion,
  FALSE,
  TRUE
)
```

Last, I want to look at the three sub-categories of consumption features (negative immediate consequences didn't have any features, which is why I leave it out from now on).
```{r visualize_sub_features}
working_file %>% 
  # only select foods and the four sub-categories
  select(
    food_id,
    food,
    sensory_proportion,
    positive_proportion,
    contextual_proportion
  ) %>% 
  group_by(food) %>% 
  slice(1) %>% 
  ungroup() %>% 
  # turn into wide format for pivoting later
  pivot_longer(
    cols = c(-food_id, -food),
    names_to = c("feature_type", ".value"),
    names_sep = "_"
  ) %>% 
  ggplot(
    aes(x = proportion)
  ) +
  geom_density(color = "darkgrey", fill = "darkgrey") + 
  facet_wrap(~ feature_type)
  
```

Alright, next I visualize the three main feature categories by food category, starting with consumption features.
```{r consumption_by_food_type}
three_violins(working_file, consumption_proportion)
summary_stats(working_file, consumption_proportion)
```

Next non-consumption features.
```{r non_consumption_by_food_type}
three_violins(working_file, non_consumption_proportion)
summary_stats(working_file, non_consumption_proportion)
```

Followed by situation-independent features.
```{r independent_by_food_type}
three_violins(working_file, situation_independent_proportion)
summary_stats(working_file, situation_independent_proportion)
```

The same for the four sub-categories, starting with sensory and action features.
```{r sensory_by_food_type}
three_violins(working_file, sensory_proportion)
summary_stats(working_file, sensory_proportion)
```

Next: Positive immediate consequences.
```{r positive_by_food_type}
three_violins(working_file, positive_proportion)
summary_stats(working_file, positive_proportion)
```

Contexutal features.
```{r contextual_by_food_type}
three_violins(working_file, contextual_proportion)
summary_stats(working_file, contextual_proportion)
```
